Channel Shaping Using Beyond Diagonal Reconfigurable Intelligent Surface:\\Analysis, Optimization, and Enhanced Flexibility

### 2025-02-11 review/response_241203.tex

\documentclass[
	fontsize=11pt,
	paper=a4,
	foldmarks=false
]{scrartcl}

\input{../manuscript/preamble}
\usepackage{response}

\setkomavar{signature}{Yang Zhao, Hongyu Li, Bruno Clerckx, and Massimo Franceschetti}
\setkomavar{date}{\today}
\setkomavar{subject}{Response to Decision on Manuscript T-SP-32387-2024}

\begin{document}
\begin{letter}{%
		Prof. Wei Yi\\
		Associate Editor\\
		IEEE Transactions on Signal Processing
	}
	\opening{Dear Editor and Reviewers,}
	Thank you for giving us the opportunity to submit a revised version of T-SP-32387-2024.
	Your comments and suggestions have been invaluable in helping us improve the quality of the manuscript.
	Below we prepare a point-to-point response and highlight the corresponding in-text changes, where labels have been matched to the latest version for your convenience.
	The title has been changed to \emph{MIMO Channel Shaping and Rate Maximization Using Beyond Diagonal RIS} to better reflect the content of the manuscript.
	We hope that the revisions and clarifications make the manuscript meet the standards of TSP publications.
	\closing{Yours sincerely,}
\end{letter}

### 2025-02-11 assets/simulation/pc_power_sx_txrx16_nd.tex
:construction: Updating results

\begin{axis}[%
width=7.607cm,
height=6cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymin=0,
ymax=0.000116439758271769,
ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor2, forget plot] table[row sep=crcr]{%
x	y\\
5	8.18421179472296e-07\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor4, forget plot] table[row sep=crcr]{%
x	y\\
6	2.47795062804422e-06\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor6, forget plot] table[row sep=crcr]{%
x	y\\
7	8.20088397806638e-06\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor8, forget plot] table[row sep=crcr]{%
x	y\\
8	2.94451091720999e-05\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor10, forget plot] table[row sep=crcr]{%
x	y\\
9	0.000111552731718914\\
};
\addplot[draw=none, only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor12] table[row sep=crcr]{%
x	y\\
0	0\\
};
\addlegendentry{Explicit}

>>>>

\begin{axis}[%
width=7.607cm,
height=6cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
% xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymin=0,
ymax=0.000116439758271769,
% ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor2, forget plot] table[row sep=crcr]{%
x	y\\
5	8.18421179472296e-07\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor4, forget plot] table[row sep=crcr]{%
x	y\\
6	2.47795062804422e-06\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor6, forget plot] table[row sep=crcr]{%
x	y\\
7	8.20088397806638e-06\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor8, forget plot] table[row sep=crcr]{%
x	y\\
8	2.94451091720999e-05\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor10, forget plot] table[row sep=crcr]{%
x	y\\
9	0.000111552731718914\\
};
\addplot[draw=none, only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor12] table[row sep=crcr]{%
x	y\\
0	0\\
};
\addlegendentry{Explicit}
